; This plugin configures item mods loaded by the itms_manager script file.

[backpack_stash]
allow_in_base = true
enable = true
enable_news_tip = true
enable_ui = true
map_spot = treasure_player

[sleeping_bag]
dangerous_sleep = false ; Enable hostile squads to hunt actor if he sleeps in unsafe area. Disabled as there are no safe spots.
enable = true
have_at_start = false ; Self-explanatory, whether the player starts with a sleeping bag in inventory
unsafe_radius = 10000 ; The distance in which hostile squads will be drawn to actor if he sleeps in unsafe area.
use_placeable = true ; Whether the items is placed at the player's location instead of using the item directly.

[sleeping_bag_sections]
itm_sleepbag
sleep_bag

[sleeping_bag_ph_sections]
ph_sleepbag = itm_sleepbag

[actor_backpack_keep_items]
af_baloon
af_blood
af_compass
af_cristall
af_cristall_flower
af_dummy_battery
af_dummy_dummy
af_dummy_glassbeads
af_electra_flash
af_electra_moonlight
af_electra_sparkler
af_eye
af_fire
af_fireball
af_fuzz_kolobok
af_glass
af_gold_fish
af_gravi
af_ice
af_medusa
af_mincer_meat
af_night_star
af_oasis_heart
af_soul
af_quest_b14_twisted
af_vyvert
bandage
bolt
device_flashlight
device_pda
device_torch
device_torch_dummy
drug_anabiotic
drug_antidot
drug_coagulant
drug_psy_blockade
drug_radioprotector
jup_b1_half_artifact
medkit
medkit_army
medkit_scientic

[repair_mod]
enable = true
use_ui = false ; Determines whether the clunky interface is used instead of new drag-and-drop callbacks.

[repair_mod_tools]
itm_gunsmith_toolkit
itm_outfit_toolkit

[flashlight_mod]
enable = false

[flashlight_sections]
device_flashlight

[mutant_loot_mod]
decay_time = 2700 ; Number of seconds (game time) after which a mutant corpse becomes too decayed to field dress.
enable = true
enable_ui = false ; Determines whether an interface is used to harvest mutant parts.

; Mutant loot sections.
; Usage: section, quantity, chance.
; See itms_manager.loot_mutant for implementation.

[rat]
mutant_part_tushkano_meat, 1, 0.75

[crow]
mutant_part_crow_beak, 1, 0.50

[bloodsucker]
mutant_part_krovosos_jaw, 1, 0.66
mutant_part_krovosos_meat, 2, 0.75

[boar]
mutant_part_boar_chop, 2, 0.66
mutant_part_boar_leg, 4, 0.25

[burer]
mutant_part_burer_hand, 2, 0.75

[chimera]
mutant_part_chimera_claw, 8, 0.33
mutant_part_chimera_kogot, 4, 0.55
mutant_part_chimera_meat, 2, 0.80

[controller]
mutant_part_controller_glass, 1, 0.75
mutant_part_controller_hand, 2, 0.66

[dog]
mutant_part_dog_meat, 2, 0.45
mutant_part_dog_tail, 1, 0.33

[flesh]
mutant_part_flesh_eye, 2, 0.5
mutant_part_flesh_meat, 3, 0.66

[gigant]
mutant_part_pseudogigant_eye, 2, 0.75
mutant_part_pseudogigant_hand, 2, 0.75

[psy_dog]
mutant_part_psevdodog_meat, 2, 0.75
mutant_part_psevdodog_tail, 1, 0.75

[pseudodog]
mutant_part_psevdodog_meat, 2, 0.66
mutant_part_psevdodog_tail, 1, 0.5

[snork]
mutant_part_snork_hand, 2, 0.33
mutant_part_snork_leg, 2, 0.45

[tushkano]
mutant_part_tushkano_head, 1, 0.5
mutant_part_tushkano_meat, 1, 0.66

[cat]
mutant_part_cat_tail, 1, 0.66

[fracture]
mutant_part_fracture_hand, 2, 0.66

[zombie]
mutant_part_zombi_hand, 2, 0.5

[karlik]
mutant_part_karlik_ear, 2, 0.5
