; This plugin lists news tips icons used for in-game news posts.
; The value of each key should be the texture to display.

[news_tips_icons]
; Achievements.
completionist = ui_inGame2_PD_Drug_Stalkerov
down_to_earth = ui_inGame2_PD_DownToEarth
duga_free = ui_inGame2_PD_Pervootkrivatel
geologist = ui_inGame2_PD_Opitniy_stalker
heavy_pockets = ui_inGame2_PD_Sostoyatelniy_klient
infopreneur = ui_inGame2_PD_Torgovets_informatsiey
mechanized_warfare = ui_inGame2_PD_master_boevih_sistem
patriarch = ui_inGame2_PD_Lider
radiotherapy = ui_inGame2_PD_Otmecheniy_zonoy
rag_and_bone = ui_inGame2_PD_RagAndBone
scholar = ui_inGame2_PD_Hranitel_tayn
silver_or_lead = ui_inGame2_PD_Avtoritet
tourist = ui_inGame2_PD_Tourist
well_dressed = ui_inGame2_PD_Ohotnik_na_mutantov
wishful_thinking = ui_inGame2_PD_WishfulThinking

; Item transfers.
got_artefact = ui_inGame2_D_gonets_pravosudiya
got_ammo = ui_inGame2_D_Ohotnik_na_mutantov
got_medicine = ui_inGame2_D_Sisshik
got_duty_light_armor = ui_inGame2_D_Vipolnil_2_zadaniya_dlya_Dolga
got_duty_heavy_armor = ui_inGame2_D_Vipolnil_4_zadaniya_dlya_Dolga
got_freedom_light_armor = ui_inGame2_D_Vipolnil_2_zadaniya_dlya_Swobodi
got_freedom_heavy_armor = ui_inGame2_D_Vipolnil_4_zadaniya_dlya_Swobodi

; Misc. gameplay.
can_resupply = ui_inGame2_Pered_zadaniyami_voennih
guide_unlock = ui_inGame2_Poslednie_razrabotki
rank_change = ui_inGame2_V_poiskah_Soroki
rep_change = ui_inGame2_PD_storonnik_ravnovesiya
recent_surge = ui_inGame2_V_zone_nedavno_proshel_vibros

; Story mode.
saharov = ui_iconsNpc_ucheniy_2
ecolog = ui_iconsNpc_ecolog
trader = ui_iconsNpc_trader
army = ui_iconsNpc_stalker_neytral_balon_6
barman = ui_iconsNpc_barman
wolf = ui_iconsNpc_stalker_neytral_balon_1

; Dynamic news.
dolg = ui_icon_news_news_dolg
freedom = ui_icon_news_news_svoboda
army = ui_icon_news_news_voen_stalk
stalker = ui_iconsTotal_grouping
csky = ui_iconsTotal_grouping
killer = ui_icon_news_news_naim
bandit = ui_icon_news_news_bandos
deth = ui_icon_news_deth
all = ui_icon_news_all
signal = ui_inGame2_Istoriya_dolga
surge = ui_inGame2_Vibros
default = ui_iconsTotal_grouping
